### 2023-09-18 2.State/lstm.tex
Couldn't really work, very bad day...

Figure \ref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then activated with either a tanh or a sigmoid activation function. Each input to the cell is a vector.
Those vector are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden state (sometimes refered to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

The equations of an LSTM are quite unusual.
Let's start with the more classic gate equations. They are the ones that behave like the more classic \ac{NN}.
The input (equation \ref{eq:inputG}), forget (equation \ref{eq:forgetG}) and ouput (equation \ref{eq:ouputG}) gates are described below.

@@

For the next equation describes the candidate cell state (equation \ref{eq:candCell}), that will next become the cell state (equation \ref{eq:cellS}).

@@

The final step of the \ac{LSTM} is to compute the hidden state (equation \ref{eq:hiddenS}).
\begin{equation}\label{eq:hiddenS}
  h_t=o_t\cdot tanh(c_t)
\end{equation}

>>>>

\Cref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then activated with either a tanh or a sigmoid activation function. Each input to the cell is a vector.
Those vector are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden state (sometimes refered to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

The equations of an LSTM are quite unusual.
Let's start with the more classic gate equations. They are the ones that behave like the more classic \ac{NN}.
The input (\cref{eq:inputG}), forget (\cref{eq:forgetG}) and ouput (\cref{eq:ouputG}) gates are described below.

@@

For the next equation describes the candidate cell state (\cref{eq:candCell}), that will next become the cell state (\cref{eq:cellS}).

@@

The final step of the \ac{LSTM} is to compute the hidden state (\cref{eq:hiddenS}).
\begin{equation}\label{eq:hiddenS}
  h_t=o_t\cdot tanh(c_t)
\end{equation}
